\hypertarget{ccc-semantics}{%
\section{CCC-Semantics}\label{ccc-semantics}}

This is a formalisation of the interpretation of the simply-typed lambda
calculus into cartesian closed categories.

\hypertarget{structure}{%
\subsection{Structure}\label{structure}}

The project is split into two parts.

\begin{itemize}
\tightlist
\item
  \texttt{CCCSemantics.Lambda}, which contains formalisation of the
  syntax, i.e.~simply typed lambda calculus, together with
  substitutions.
\item
  \texttt{CCCSemantics.Categories}, a small library for category theory,
  formalising up to and including the Yoneda lemma, as well as the
  notion of CCCs.
\end{itemize}

\hypertarget{cccsemantics.lambda}{%
\subsubsection{\texorpdfstring{\texttt{CCCSemantics.Lambda}}{CCCSemantics.Lambda}}\label{cccsemantics.lambda}}

\hypertarget{cccsemantics.categories}{%
\subsubsection{\texorpdfstring{\texttt{CCCSemantics.Categories}}{CCCSemantics.Categories}}\label{cccsemantics.categories}}

The category theory library defines categories
(\texttt{Categories/Category.lean}) using a \emph{bundled}
representation, rather than following Mathlib's definition using
type-classes. For better inference of operators in specific choices of
categories, such as product categories, we use \texttt{unif\_hint}s.
This is not necessarily a better choice, but was more an experiment to
see how well such a library would work.

Functors (\texttt{Categories/Functor.lean}) and natural transformations
(\texttt{Categories/NaturalTransformation.lean}) are defined as
standard, and by making use of the bundled representation we are able to
more easily define certain categories, such as \texttt{Cat} the category
of categories (\texttt{Categories/Instances/Cat.lean}).

We also define functor categories
(\texttt{Categories/Instances/Func.lean}) and the category of types
(\texttt{Categories/Instances/Types.lean}), so we have the category of
presheaves. This then allows us to construct the Yoneda-embedding, which
we make use of to show that presheaf categories are cartesian closed
(\texttt{Categories/CartesianClosed/Presheaf.lean}). We prove the Yoneda
lemma as a nice result, but it is not used for the rest of the
formalisation.

We also define adjunctions (\texttt{Categories/Adjunction.lean}), using
the unit-counit definition. There is a construction of adjunctions from
the definition of naturally hom-set \texttt{Hom\ (F\ -)\ -} and
\texttt{Hom\ -\ (G\ -)} as well, which is used to construct the
hom-product adjunction for cartesian closed categories.

For cartesian categories (\texttt{Categories/CartesianClosed.lean}) we
use the elementary definition, requireing an assignment for each pair of
objects to a product, defined explicitly, rather than through a general
interface for limits. This is defined as a type-class indexed by
categories. We define cartesian closed category as an extended
type-class on cartesian categories, additionally having an assignment of
exponentials to each pair of objects. We show how both the assigment of
products and of exponentials give functors, and that these are adjoint
as expected. We show that the category of types
(\texttt{Categories/CartesianClosed/Types.lean}) and, as mentioned
earlier, presheaf categories, are cartesian closed.
